---
title: "Gene Expression Analysis of Rat Testis Across Developmental Stages"
author: "Brad Hansen"
date: "3/24/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# **Gene Expression Analysis of Rat Testis Across Developmental Stages**

### Data from [NCBI GEO](https://www.ncbi.nlm.nih.gov/geo/)

Data used:

> GEO study [GSE108348](https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE108348)
>
>> Study GSE108348 includes transcriptomes from three species, four organs, across five developmental stages. This project considers the 

> GEO study XXXYYYZZZ
>
>> Study XXXYYYZZZ includes...

> GEO study XXXYYYZZZ
>
>> Study XXXYYYZZZ includes...

> GEO study XXXYYYZZZ
>
>> Study XXXYYYZZZ includes...

> GEO study XXXYYYZZZ\
>
>> Study XXXYYYZZZ includes...





```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
